On the robustness of phylogeographic inference to model assumptions

### 2024-06-01 manuscript/phylogeo.tex
move figures around

\begin{document}
\title{When to trust phylogeographic inferences?}
\author{Richard Neher}
\date{\today}
\begin{abstract}
    Sometimes.
\end{abstract}

>>>>

\begin{document}
\title{On the robustness of phylogeographic inference to model assumptions}
\author{Richard A.~Neher}
\date{\today}
\begin{abstract}
Phylogeographic inference in continuous space is a popular method to reconstruct the spatial distribution of ancestral populations and estimate parameters of the dispersal process.
While the underlying probabilistic models can be complex and computationally demanding to infer, they typically ignore that replication and population growth are tightly coupled to spatial location.
Such coupling, in particular when habitats change over time, can result in biased and overconfident estimates of ancestral locations and dispersal parameters.
These distortions depend in complicated ways the past dynamics of habitats and underlying population dynamics and dispersal processes such that validity of phylogeographic inferences is hard to assess.
\end{abstract}
